---
title: "BF_HW_ARIMA"
author: "sp2245@scarletmail.rutgers.edu"
date: "11/10/2022"
output: html_document
---
```{r}
library(fpp)
library(fpp2)
library(forecast)

## Data set- fdeaths
#### fdeaths plot
fdeaths
plot(fdeaths, main = 'No of Deaths caused', xlab = 'Year', ylab = 'count')


```

* We can observe that the data  has seasonality.

### Window plot

```{r}
deaths_win <- window(fdeaths, start = 1976)
plot(deaths_win, main = 'No of Deaths caused', xlab = 'Year', ylab = 'count')

```

* We can observe that after  applying windows fucntion and taking a window from 1976  to the data, we still see seasonality in the data.

#### Acf plot

```{r}
Acf(deaths_win, main = 'Acf Plot - deaths from 1976')
```
*We see seasonality after using the Acf function as well.

## ARIMA for data with seasonal component

#### Checking the Differencing needed for seasonal component

nsdiffs(deaths_win) # nsdiffs is for seasonal

#nsdiffs is use to know how many differences we need to do for seasonality component.


#### Checking the Differences needed

ndiffs(deaths_win)
# We got the ndiffs as 0

#### Rechecking the differencing needed after performing the seasonal differencing.

ndiffs((diff(deaths_win,12)))
# The ndiffs still shows as 0.

#### Acf and Pacf plots

```{r}
tsdisplay(diff(fdeaths,12))
```
* In the Acf plot we can see that the p value is 2.

#### Arima Model

```{r}
arima_fit <- auto.arima(deaths_win,trace=TRUE, stepwise = FALSE )
arima_fit
```
 * The system runs the auto arima and gives out the best model for which the AIC value is the lowest. The AIC value is 422.71 and the ARIMA(2,0,1)(1,1,0)[12].

#### Arima Model attributes
 
```{r}
attributes(arima_fit)
```

#### Plotting forecast of the Arima model with 99.5% confidence

```{r}
plot(forecast(arima_fit,h=5,level=c(99.5)), main = 'Forecast of the ARIMA model', xlab = 'Year', ylab = 'Count')
```


## Residual Analysis

#### Acf of Residuals

```{r}
Acf(arima_fit$residuals)
```
 * We can observe that none of the data passes the confidence interval limits.
* Which means that the forecast is a good forecast.

#### Box-Ljung test
```{r}
Box.test(residuals(arima_fit), lag=20, type="Ljung")

```
 * The p-value is greater than 0.05  ( p value= 0.9079) so we can determine that  the null hypothesis is supported.
* The residuals are random.

#### Residuals plot

```{r}
plot.ts(residuals(arima_fit))
```
* The residuals appear to be random adn we can say this is a good forecasting model.

#### Histogram plot of residuals
```{r}
hist(arima_fit$residuals)
```
* We can observe that the distribution is not normally distributed and left skewed as well.


#### TSDiagram of the ARIMA model
```{r}
tsdiag(arima_fit)
```
 
 * The standardized residuals plot looks good.  We can see 3 residuals  are very close to touch.

 * There are no significant values in the Acf plot as we see there are no values above the confidence interval.

 * The p-values in Ljung-Box test are also above level and the points  are above the confidence interval line ( blue line).
* The  ARIMA model is a good fit.






